Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-08 edubots_surveys.Rnw
reviewed conclusions - last paragraphs

Our analysis of the results of this survey can be fed into several potential avenues for future research. For instance, the rollout of extensive videoconferencing and virtual
teaching solutions that the COVID pandemic has brought has also taught us a
series of lessons. It increases isolation, for instance, and decreases the
amount of synchronous contact that happens in the fringes of the classroom:
teaching staff offices, before and after class. A future line of work would be
focused on exactly this, and what kind of needs could be covered by chatbot
technology. We will create a series of international surveys that will
investigate this.

Finally, the full extent of chatbot technology is not really being examined in
these surveys. They can be connected to natural language processing engines with
sentiment analysis as well as other analytics. Examining the mood of the class,
as response to new material, assignment, exams or external events might help
will help any student-centered teaching strategy, which will help students (and
teachers) reach their learning objectives. This line of work, however, will be
based on the introduction of some pilot study, combined with initial opinion
assessment on the students.

>>>>

Our analysis of the survey results can inform several potential avenues for future research. 
For instance, the rollout of extensive videoconferencing and virtual
teaching solutions that the COVID pandemic has brought has also taught us a
series of lessons: it increases isolation, for instance, and decreases the
amount of synchronous contact that happens in the fringes of the classroom (e.g. 
teaching staff offices, or before and after class). A future line of research could 
focus on these issues and explore how chatbot technology could address them. 
%We will create a series of international surveys that will investigate this.

Finally, the full extent of chatbot technology is not really examined in
these surveys. They can be connected to natural language processing engines with
sentiment analysis as well as other analytics. Examining the mood of the class such 
as responses to new materials, assignments, exams or external events will help
any student-centered teaching strategy, which will also help students (and
teachers) achieve their learning objectives. This line of work, however, would require
the introduction of some pilot study combined with initial opinion
assessments from students.
